Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
related work section updates

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' \cite{kuhn1996structure} in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1984 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems''. This concept later evolved into a broader sense of  Computer-supported collaboration (CSC). The Social computing \cite{parameswaran2007research} is another shift, which refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in `computing' rather than `collaboration'. Similarly, the Human Computation \cite{von2009human} is another paradigm towards this computational direction, which utilize human processing power to solve problems that computers cannot yet solve. All these three mentioned fields has overlapping in the their concepts and they are mainly popularised in the computer science. In the Web 2.0 era, there are few new broader concepts/buzzword emerged on the idea of utilising the human power which are not only used in computer science, but also in other fields such as social science, business etc. For example, crowding sourcing \cite{howe2006crowdsourcing} is an idea that taking a job traditionally performed by a designated agent and outsourcing it to an undefined, generally large group of people in the form of an open call. Open Innovation \cite{chesbrough2008open} advocates the similar idea with empathising on the innovation in firms. Surowiecki also argued in the book of the wisdom of crowds \cite{surowiecki2005wisdom} that the aggregation of information in groups, resulting in decisions that are often better than could have been made by any single member of group. Collective Intelligence described by Malone \cite{malone2009harnessing}, defines a even more broadly term that ``groups of individuals doing things collectively that seem intelligent.'' 
The relationship between human computation, crowdsourcing, social computing and collective intelligence is discussed in \cite{quinn2011human}. 
In  social machines  the  social and  the  technical are equal  partners. While  crowdsourcing  could  be  viewed  as  'human  subroutines'  and  'citizen  sensors',  the social machine perspective is one of incentivised participation and not humans enslaved to computers, as described in Figure \ref{socialmachine}.

>>>>

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' \cite{kuhn1996structure} in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1984 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems''. This concept later evolved into a broader sense of  Computer-supported collaboration (CSC). The Social computing \cite{parameswaran2007research} is another shift, which refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in `computing' rather than `collaboration'. Similarly, the Human Computation \cite{von2009human} is another paradigm towards this computational direction, which utilize human processing power to solve problems that computers cannot yet solve. All these three mentioned fields overlap in their concepts and they are mainly popularised in the computer science. In the Web 2.0 era, there were few generic concepts/buzzword emerged on the idea of utilising the human power which are not only used in computer science, but also in other fields such as social science, business etc. Crowding sourcing \cite{howe2006crowdsourcing} as an example, describes the idea that taking a job traditionally performed by a designated agent and outsourcing it to an undefined, generally large group of people in the form of an open call. Open Innovation \cite{chesbrough2008open} advocates the similar idea with empathising on the innovation in firms. Surowiecki also argued in the book of the wisdom of crowds \cite{surowiecki2005wisdom} that the aggregation of information in groups, resulting in decisions that are often better than could have been made by any single member of group. Collective Intelligence described by Malone \cite{malone2009harnessing}, defines a even more broadly term that ``groups of individuals doing things collectively that seem intelligent.'' 
The relationship between human computation, crowdsourcing, social computing and collective intelligence is discussed in \cite{quinn2011human}. 
In  social machines  the  social and  the  technical are equal  partners. While  crowdsourcing  could  be  viewed  as  'human  subroutines'  and  'citizen  sensors',  the social machine perspective is one of incentivised participation and not humans enslaved to computers, as described in Figure \ref{socialmachine}.
